Trafficking synaptic cargo in complex morphologies involves tradeoffs in speed and precision

### 2015-10-20 latex/paper.tex
v5

To test the plausibility of this model in a complex morphology, we extended an existing multi-compartment model of a CA1 pyramidal neuron \citep{Migliore_2012}. Excitatory synaptic input was delivered to 120 locations within three dendritic regions (red dots, Fig. 2D), and the average membrane potential in each electrical compartment determined the target level $\tilde{u}_i$ in each compartment (Methods). This models how molecular cargo could be selectively trafficked to active synaptic sites. Figures 2E and 2F confirm that the spatial distribution of $u$ approaches the desired steady-state.

@@

>>>>

To test the plausibility of this model in a complex morphology, we incorporated it into an existing multi-compartment model of a CA1 pyramidal neuron \citep{Migliore_2012}. Excitatory synaptic input was delivered to 120 locations within three dendritic regions (red dots, Fig. 2D), and the average membrane potential in each electrical compartment determined the target level $\tilde{u}_i$ in each compartment (Methods). This models how molecular cargo could be selectively trafficked to active synaptic sites. Figures 2E and 2F confirm that the spatial distribution of $u$ approaches the desired steady-state.

@@

This work was supported by Howard Hughes Medical Institute (T.S.), NIH Grant 1P01NS079419 (E.M and T.O.), NIH Grant P41GM103712 (A.H.W., C.O. and T.S.), Charles A. King Trust (T.O.), and the Deptartment of Energy Computational Science Graduate Fellowship (A.H.W.).
